Are environmental and geographic variables effective surrogates for genetic variation in conservation planning?

### 2016-02-06 article/article.Rmd
+ reversion to adegenet + but include updates to manuscript + change 03-*.R and 04-*.R to meaningful file names

First, we grouped individuals into genetic lineages for each species. The purpose of this step was to avoid misclassifying loci as adaptive. We used Gaussian mixture models to assign individuals to populations [implemented in $\texttt{mclust}$ R package; @r477; @r467]. Briefly, for each species, we fit a suite of models to estimate the probability that individuals belonged different populations (using default priors and covariance structures). For each parametrization, we fit a set of models assuming varying numbers of total populations (\textit{G} = 1--`max(r mclust.params.LST[[MODE]]$G)`). We identified the most parsimonious models (lowest Bayesian Information Criterion $BIC$ statistic; Figures S4), and used these to group individuals into populations (Figure S5).

We identified loci under selection. For each species, we ran $\texttt{Bayescan}$ [version 2.1; @r456] using the population memberships identified in the previous analysis (1:1 prior odds; `r bayescan.params.LST[[MODE]]$nbp` pilot runs; `r bayescan.params.LST[[MODE]]$burn` burn-in iterations; `r bayescan.params.LST[[MODE]]$n` post-burn-in iterations thinned by `r bayescan.params.LST[[MODE]]$thin` iterations; Table S2). To avoid false-positive, we omitted loci where the global frequency of the minor allele was $\geq 0.05$ (following guidelines in the $\texttt{Bayescan}$ manual). Additionally, to prevent individuals with unclear ancestry from biasing this analysis, we omitted individuals if there was considerable uncertainty in their population membership (maximum probability $\leq `r mclust.params.LST[[MODE]]$probability.threshold`$ % ). We ran `r bayescan.params.LST[[MODE]]$reps` replicates per species using a suitable false discovery rate to ensure convergence [FDR $\leq `r bayescan.params.LST[[MODE]]$fdr`$; @r466].

@@

For each scenario, we generated three types of prioritizations. We generated prioritizations using only amount-based, both amount- and surrogate-based targets, and both amount- and genetic-based targets. The purely amount-based prioritizations represented those typically generated in conservation planning exercises and serve as our baseline. We used `r (rapr.params.LST[[MODE]]$amount.target*100)` % amount-based targets in all prioritizations to ensure an adequate proportion of habitat was secured for each species [@rXXX]. We set surrogate- and genetic-based targets as `r (rapr.params.LST[[MODE]]$surrogate.target*100)` % to ensure that most of the repsective variation was secured for each species. To accomodate variation in the high number of optimal solutions for the single-species amount-based prioritizations, we generated `r (rapr.parmas.LST[[MODE]]$amount.replicates)` replicate prioritizations. Since all other contexts were likely to be associated with a single optimal solution, we used only a single replicate.

>>>>

First, we grouped individuals into genetic lineages for each species. The purpose of this step was to avoid misclassifying loci as adaptive. We used discriminant analyses of principle components [DAPC; @r467] to assign individuals to populations [implemented in $\texttt{adegenet}$ R package; @r468]. Briefly, for each species, we transformed the binary loci data using a principle components analysis (PCA) and obtained the principle components required to explain at least `r adegenet.params.LST[[MODE]]$perc.pca` % variation. We subject these components to multiple \textit{k}-means clustering models with varying numbers of assumed populations (\textit{k} = 1--`r adegenet.params.LST[[MODE]]$max.n.clust`; `r adegenet.params.LST[[MODE]]$n.iter` iterations; `r adegenet.params.LST[[MODE]]$n.start` random starts). We then  applied Ward's clustering method to the Bayesian Information Criterion (BIC) statistics associated with each model to partition the models into two groups, and selected the model before the first group switch (as recommended in the \texttt{adegenet} manual; Figure S4). The populations memberships associated with these models were used for subsequent analysis (Figure S5).

We identified loci under selection. For each species, we ran $\texttt{Bayescan}$ [version 2.1; @r456] using the population memberships identified in the previous analysis (1:1 prior odds; `r bayescan.params.LST[[MODE]]$nbp` pilot runs; `r bayescan.params.LST[[MODE]]$burn` burn-in iterations; `r bayescan.params.LST[[MODE]]$n` post-burn-in iterations thinned by `r bayescan.params.LST[[MODE]]$thin` iterations; Table S2). To avoid false-positive, we omitted loci where the global frequency of the minor allele was $\geq 0.05$ (following guidelines in the $\texttt{Bayescan}$ manual). We ran `r bayescan.params.LST[[MODE]]$reps` replicates per species using a suitable false discovery rate to ensure convergence [FDR $\leq `r bayescan.params.LST[[MODE]]$fdr`$; @r466].

@@

For each scenario, we generated three types of prioritizations. We generated prioritizations using only amount-based, both amount- and surrogate-based targets, and both amount- and genetic-based targets. The purely amount-based prioritizations represented those typically generated in conservation planning exercises and serve as our baseline. We used `r (rapr.params.LST[[MODE]]$amount.target*100)` % amount-based targets in all prioritizations to ensure an adequate proportion of habitat was secured for each species [@rXXX]. We set surrogate- and genetic-based targets as `r (rapr.params.LST[[MODE]]$surrogate.target*100)` % to ensure that most of the repsective variation was secured for each species. To accomodate variation in the high number of optimal solutions for the single-species amount-based prioritizations, we generated `r (rapr.params.LST[[MODE]]$amount.replicates)` replicate prioritizations. Since all other contexts were likely to be associated with a single optimal solution, we used only a single replicate.
